Distributed Nonlinear Feedback Design with Separable Control-Contraction Metrics

### 2017-02-12 R0V0.tex
Put clique tree into the notation paragraph

\mypara Let $N>0$ be an integer, a \emph{graph} consists of a set of \emph{nodes} $\mathscr{V}\subset\mathbb{N}_{[1,N]}$ and a set of \emph{edges} $\mathscr{E}\subset\mathscr{V}\times\mathscr{V}$ and it is denoted by the pair $(\mathscr{V},\mathscr{E})=\mathscr{G}$. A node $i\in\mathscr{V}$ is said to be \emph{adjacent} to a node $j\in\mathscr{V}$ if $(i,j)\in\mathscr{E}$, the set of nodes that are adjacent to $j$ is defined as $\mathscr{N}(j)=\{i\in\mathscr{V}:i\neq j,(i,j)\in\mathscr{E}\}$. A graph is said to be \emph{undirected} if, for every edge $(i,j)\in\mathscr{E}$, there exists $(j,i)\in\mathscr{E}$. It is said to be \emph{directed} if otherwise. Given two nodes $i,j\in\mathscr{V}$, an ordered sequence of edges $\left\{(k,k+1)\right\}_{k=i}^{j-1}$ is said to be a \emph{path from the node $i$ to the node $j$}. A path is said to be \emph{cycle} if no edges are repeated and the nodes $i$ and $j-1$  are distinct. A graph is said to be \emph{strongly connected} if, for every two nodes $i,j\in\mathscr{V}$, there exists a path connecting them. It is also said to be \emph{complete} is every node is adjacent to any other node, and it is \emph{incomplete} otherwise. A graph is said to be a \emph{tree} if it is connected and does not contain cycles. A \emph{leaf} is a node that is adjacent to only one node.

@@

\mypara Some concepts of graph theory and semidefinite programming are recalled from \cite{PakazadHanssonAndersenEtAl2015,VandenbergheAndersen2015,BlairPeyton1993}. Consider the graph $\mathscr{G}=(\mathscr{V},\mathscr{E})$ describing the topology of the network~\eqref{eq:general system}. A \emph{clique} $\mathscr{C}\subset\mathscr{V}$ of the graph $\mathscr{G}$ is the maximal set of nodes that induces a complete subgraph on $\mathscr{G}$. A \emph{chord} of a path is any edge joining two nonconsecutive nodes. A graph is said to be \emph{chordal} if every cycle greater than three has a chord. The importance of a graph being chordal is that it has a tree-decomposition into cliques  \cite[Proposition~12.3.11]{Diestel2005} such a tree is said to be a \emph{clique tree} and it is denoted as $\mathscr{T}(\mathscr{G})$.

@@

\begin{table}
	\begin{tabular}{r|l}
	Method&Time taken by the solver (4 agents)\\ \hline
	Chordal graph decomposition&7.4s (unconstrained)\\
	&7.7s (neighbor)\\
	&6.2s (decentralized)\\	
	ADMM&114s\\\hline
	\end{tabular}
	\caption{A summary of the time taken to solve the matrix inequality~\eqref{eq:MI formulation} using chordal graph decomposition, in the topology illustrated by Fig.~\ref{fig:cycle graph}.}
	\label{tab:cyclic case}
\end{table}

>>>>

\mypara Let $N>0$ be an integer, a \emph{graph} consists of a set of \emph{nodes} $\mathscr{V}\subset\mathbb{N}_{[1,N]}$ and a set of \emph{edges} $\mathscr{E}\subset\mathscr{V}\times\mathscr{V}$ and it is denoted by the pair $(\mathscr{V},\mathscr{E})=\mathscr{G}$. A node $i\in\mathscr{V}$ is said to be \emph{adjacent} to a node $j\in\mathscr{V}$ if $(i,j)\in\mathscr{E}$, the set of nodes that are adjacent to $j$ is defined as $\mathscr{N}(j)=\{i\in\mathscr{V}:i\neq j,(i,j)\in\mathscr{E}\}$. A graph is said to be \emph{undirected} if, for every edge $(i,j)\in\mathscr{E}$, there exists $(j,i)\in\mathscr{E}$. It is said to be \emph{directed} if otherwise. Given two nodes $i,j\in\mathscr{V}$, an ordered sequence of edges $\left\{(k,k+1)\right\}_{k=i}^{j-1}$ is said to be a \emph{path from the node $i$ to the node $j$}. A path is said to be \emph{cycle} if no edges are repeated and the nodes $i$ and $j-1$  are distinct. A graph is said to be \emph{strongly connected} if, for every two nodes $i,j\in\mathscr{V}$, there exists a path connecting them. It is also said to be \emph{complete} is every node is adjacent to any other node, and it is \emph{incomplete} otherwise. A graph is said to be a \emph{tree} if it is connected and does not contain cycles. A \emph{leaf} is a node that is adjacent to only one node. The following concepts are recalled from \cite{PakazadHanssonAndersenEtAl2015,VandenbergheAndersen2015,BlairPeyton1993}. A \emph{clique} $\mathscr{C}\subset\mathscr{V}$ of the graph $\mathscr{G}$ is the maximal set of nodes that induces a complete subgraph on $\mathscr{G}$. A \emph{chord} of a path is any edge joining two nonconsecutive nodes. A graph is said to be \emph{chordal} if every cycle greater than three has a chord. The importance of a graph being chordal is that it has a tree-decomposition into cliques  \cite[Proposition~12.3.11]{Diestel2005} such a tree is said to be a \emph{clique tree} and it is denoted as $\mathscr{T}(\mathscr{G})$.

@@

@@

\begin{table}
	\begin{tabular}{r|l}
	Method&Time taken by the solver (4 agents)\\ \hline
	Chordal graph decomposition&7.4s (unconstrained)\\
	&7.7s (neighbor)\\
	&6.2s (decentralized)\\\hline
	\end{tabular}
	\caption{A summary of the time taken to solve the matrix inequality~\eqref{eq:MI formulation} using chordal graph decomposition, in the topology illustrated by Fig.~\ref{fig:cycle graph}.}
	\label{tab:cyclic case}
\end{table}
